Reproducibility in Plant Pathology

### 2019-05-20 README.rmd
Update README

Or you can install this compendium as an R package, Reproducibility.in.Plant.Pathology, from GitHub with:
```{r gh-installation, eval = FALSE}
if (!require("remotes")) install.packages("remotes")
remotes::install_github("openplantpathology/Reproducibility_in_Plant_Pathology")
```

@@

The package has a number of dependencies on other R packages, and programs
outside of R. These are listed at the bottom of this README. Installing these
can be time-consuming and complicated, so we've provided a Docker image that
includes all the necessary software, code and data to run our analysis. The
Docker image may give a quicker entry point to the project, and is more
self-contained, so might save some fiddling with installing things.

#### The Docker image

A Docker image is a lightweight GNU/Linux virtual computer that can be run as a
piece of software on Windows and OSX (and other Linux systems). To capture the
complete computational environment used for this project we have a Dockerfile
that specifies how to make the Docker image that we developed this project in.
The Docker image includes all of the software dependencies needed to run the
code in this project, as well as the R package and other compendium files. To
launch the Docker image for this project, first,
[install Docker](https://docs.docker.com/installation/) on your computer. At the
Docker prompt, enter:

    docker run -dp 8787:8787 adamhsparks/reproducibility_in_plant_pathology

This will start a server instance of RStudio. Then open your web browser at
localhost:8787 or or run `docker-machine ip default` in the shell to find the
correct IP address, and log in with rstudio/rstudio.

Once logged in, use the Files pane (bottom right) to navigate to
`Reproduciblity_in_Plant_Pathology` folder for this project, and open the
`.Rproj` file for this project. Once that's open, you'll see the
`analysis/paper` directory in the Files pane where you can find the R markdown
document, and knit them to produce the results in the paper. More information
about using RStudio in Docker is available at the
[Rocker](https://github.com/rocker-org)
[wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

We developed and tested the package on this Docker container, so this is the
only platform that we're confident it works on, and so recommend to anyone
wanting to use this package to generate the vignettes, etc.

@@

We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
17.10.

@@

(+61) (7) 4831 1948   adam.sparks@usq.edu.au
https://staffprofile.usq.edu.au/Profile/Adam-Sparks

>>>>

Or you can install this compendium as an R package, Reproducibility.in.Plant.Pathology, from GitHub with:
```{r gh-installation, eval = FALSE}
if (!require("remotes"))
  install.packages("remotes")
remotes::install_github("openplantpathology/Reproducibility_in_Plant_Pathology"
)
```

@@

@@

@@

+61 (7) 4831 1948   <adam.sparks@usq.edu.au>

<https://adamhsparks.netlify.com/>
